### 2022-11-07 manuscript.Rmd
Use split experiments when available
Using mixed experiments by default would bias the beta for gender

# We go ahead with the last solution (i.e., prefer mixed experiments) as to use
# the maximum amount of information while not biasing the gender results
dat_meta <- dat_both_mixed

@@

```{r child = "supplement.Rmd"}
```

>>>>

# We go ahead with the last solution (i.e., prefer split experiments) as to use
# the maximum amount of information while not biasing the gender results
dat_meta <- dat_both_split

@@

```{r child = "supplement.Rmd"}

```
